---
title: "R Notebook"
output: html_notebook
---

Tidyverse consolidation homework

3 MVP
1. Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
library(tidyverse)
```


```{r}
codeclan_tweets <- read_csv("data/code_clan_tweets.csv")
```

```{r}
dim(codeclan_tweets)
nrow(codeclan_tweets)
names(codeclan_tweets)
head(codeclan_tweets)
#glimpse(codeclan_tweets)
tail(codeclan_tweets)
view(codeclan_tweets)
```

2. First, we’re going to summarise the number of likes (favorite_count) CodeClan tweets have. Create a boxplot to check for outliers.

```{r}
favourite <- codeclan_tweets %>%
  select(favorite_count) 
  #summarise(x = sum(favourite))

boxplot(favourite)
```

3. Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).


```{r}
total_favourtied_tweets <- codeclan_tweets %>%
  filter(is_quote == FALSE) %>%
  summarise(sum(favorite_count)) 
  
total_favourtied_tweets

```

4. Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
mean_retweets <- codeclan_tweets %>%
  filter(is_quote == FALSE) %>%
  group_by(source) %>%
  summarise(mean_re_tweets = mean(retweet_count)) %>%
  arrange(desc(mean_re_tweets))

mean_retweets
```

5. Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
unique(codeclan_tweets$media_type)
```

```{r}
total_likes <- codeclan_tweets %>%
  #filter(is_quote == FALSE) %>%
  group_by(media_type) %>%
  summarise(likes = sum(favorite_count)) %>%
  #mutate()
  arrange(desc(likes))

total_likes
          
```

6. Find the mean number of characters that a CodeClan tweet contains.

```{r}
mean_characters_tweet <- codeclan_tweets %>%
  select(tweet_id, user_id, text)%>%
  group_by(text) %>%
  mutate(text_num = nchar(text))
  
mean_characters_tweet
nchar(text)
```



7. The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
codeclan_info <- read_csv("data/code_clan_info.csv")
```

```{r}
dim(codeclan_info)
nrow(codeclan_info)
names(codeclan_info)
head(codeclan_info)

```


```{r}
joined_codeclan_tibbles <- codeclan_tweets %>%
  #add_column(status_url = codeclan_info$status_url)
  #mutate(bind_cols(codeclan_tweets, codeclan_info))
  mutate(inner_join(codeclan_tweets, codeclan_info, by = "tweet_id"))
names(joined_codeclan_tibbles)
head(joined_codeclan_tibbles)
```


8. From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.

```{r}
codeclan_hashtags <- joined_codeclan_tibbles %>%
  select(tweet_id, hashtags) %>%
  filter(is.na(hashtags) == FALSE, str_detect(hashtags, "[A-Z]", negate = TRUE))
  #arrange()
codeclan_hashtags
```









