---
title: "R Notebook"
output: html_notebook
---

```{r}
library(car)
library(tidyverse)
library(modelr)
library(GGally)
```

```{r}
houses_data <- read_csv("data/kc_house_data.csv")
```

```{r}
summary(houses_data)
```

```{r}
glimpse(houses_data)
```

# Tidy up the data ready for regression


```{r}
unique(houses_data$condition)
unique(houses_data$grade)
unique(houses_data$view)
```

Removing date, id, sqft_living15, sqft_lot15 and zipcode 
Convert Waterfront to logical 
Converted yr_renovated into a renovated logical variable, indicating whether the property had ever been renovated. 
Convert condition and grade to factor because they are categorical


```{r}
houses_tidy <- houses_data %>%
  select(-c("id", "date", "sqft_living15", "sqft_lot15", "zipcode")) %>%
  mutate(waterfront = as.logical(waterfront)) %>%
  mutate(renovated = yr_renovated != 0) %>%
  select(-"yr_renovated") %>%
  mutate(condition = as_factor(condition)) %>%
  mutate(grade = as_factor(grade))

glimpse(houses_tidy)
  
```

Check for aliased variables using the alias() function (this takes in a formula object and a data set). [Hint - formula price ~ . says ‘price varying with all predictors’, this is a suitable input to alias()]. Remove variables that lead to an alias. Check the ‘Elements of multiple regression’ lesson for a dropdown containing further information on finding aliased variables in a dataset.

```{r}
alias(price ~ ., data = houses_tidy)
```

The output says that sqft_basement can be calculated as 
intercept + sqft_living - sqft_above
So we can drop sqft_basement


```{r}
houses_tidy <- houses_tidy %>%
  select(-c("sqft_basement"))

glimpse(houses_tidy)
```


Systematically build a regression model containing up to four main effects (remember, a main effect is just a single predictor with coefficient), testing the regression diagnostics as you go 

splitting datasets into numeric and non-numeric columns might help ggpairs() run in manageable time, although you will need to add either a price or resid column to the non-numeric dataframe in order to see its correlations with the non-numeric predictors.

```{r}
houses_tidy_numeric <- houses_tidy %>%
  select_if(is.numeric)

ggpairs(houses_tidy_numeric)
```


Correlation of sqft_living with price looks pretty promising

```{r}
houses_tidy_nonnumeric <- houses_tidy %>%
  select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- houses_tidy$price

ggpairs(houses_tidy_nonnumeric)

```

The split of price by grade and waterfront also look decent.

```{r}
houses_tidy %>%
  ggplot(aes(x = grade, y = price)) +
  geom_boxplot()
```

```{r}
houses_tidy %>%
  ggplot(aes(x = waterfront, y = price)) +
  geom_boxplot()
```


```{r}
gggpairs(housing_test)
ggpairs(housing_test1)
```

The ggpairs plots reveal that sqft_living strongly corelated with price.
Also, The split of price by grade appears to be strongly influenced.


FIRST PREDICTOR
Now, lets start with sqft_living.

```{r}
mod1a <- lm(price ~ sqft_living, data = houses_tidy)
summary(mod1a)
```

The regression equation is 
Price = -43580.7 + 280.6 * sqft_living

```{r}
mod1b <- lm(price ~ grade, data = houses_tidy)
summary(mod1b)
```



```{r}
mod1c <- lm(price ~ waterfront, data = houses_tidy)
summary(mod1c)
```


# grade looks the most promising, but some of the grade level coeffs are insignificant.
# the F-test at the bottom of the regression output tests against the null model (i.e. intercept only)
# but, if we want, we can replicate this using a separate anova
# null model: regress price on intercept only

```{r}
null_model <- lm(price ~ 1, data = houses_tidy)
grade_model <- lm(price ~ grade, data = houses_tidy)
anova(null_model, grade_model)
```

# grade is significant, let's keep it. Now plot diagnostics

```{r}
par(mfrow = c(2, 2))
plot(mod1b)
```

SECOND PREDICTOR

```{r}
houses_resid <- houses_tidy %>%
  add_residuals(mod1b) %>%
  select(-c("price", "grade"))

houses_resid_numeric <- houses_resid %>%
  select_if(is.numeric)

houses_resid_nonnumeric <- houses_resid %>%
  select_if(function(x) !is.numeric(x))

houses_resid_nonnumeric$resid <- houses_resid$resid
```


```{r}
ggpairs(houses_resid_numeric)
```


```{r}
ggpairs(houses_resid_nonnumeric)
```


lat has highest correlation with residuals, but, again, waterfront still looks pretty promising. Try both…

```{r}
mod2a <- lm(price ~ grade + lat, data = houses_tidy)
summary(mod2a)
```

```{r}
mod2b <- lm(price ~ grade + waterfront, data = houses_tidy)
summary(mod2b)
```

```{r}
par(mfrow = c(2, 2))
plot(mod2a)
```

THIRD PREDICTOR

```{r}
houses_resid <- houses_tidy %>%
  add_residuals(mod2a) %>%
  select(-c("price", "grade", "lat"))

houses_resid_numeric <- houses_resid %>%
  select_if(is.numeric)

houses_resid_nonnumeric <- houses_resid %>%
  select_if(function(x) !is.numeric(x))

houses_resid_nonnumeric$resid <- houses_resid$resid
```


```{r}
ggpairs(houses_resid_numeric)
```


```{r}
ggpairs(houses_resid_nonnumeric)
```

Now view has strongest correlation with residuals, but also compare against model with waterfront.


```{r}
mod3a <- lm(price ~ grade + lat + view, data = houses_tidy)
summary(mod3a)
```

```{r}
par(mfrow = c(2, 2))
plot(mod3a)
```

FOURTH PREDICTION

```{r}
houses_resid <- houses_tidy %>%
  add_residuals(mod3a) %>%
  select(-c("price", "grade", "lat", "view"))

houses_resid_numeric <- houses_resid %>%
  select_if(is.numeric)

houses_resid_nonnumeric <- houses_resid %>%
  select_if(function(x) !is.numeric(x))

houses_resid_nonnumeric$resid <- houses_resid$resid
```

```{r}
ggpairs(houses_resid_numeric)
```


```{r}
ggpairs(houses_resid_nonnumeric)
```

sqft_living has highest correlation with residuals. Let’s test against all remaining categorical predictors:


```{r}
mod4a <- lm(price ~ grade + lat + view + sqft_living, data = houses_tidy)
summary(mod4a)
```

```{r}
mod4b <- lm(price ~ grade + lat + view + waterfront, data = houses_tidy)
summary(mod4b)
```

```{r}
mod4c <- lm(price ~ grade + lat + view + condition, data = houses_tidy)
summary(mod4c)
```

```{r}
mod4d <- lm(price ~ grade + lat + view + renovated, data = houses_tidy)
summary(mod4d)
```


```{r}
par(mfrow = c(2, 2))
plot(mod4a)
```


```{r}
houses_resid <- houses_tidy %>%
  add_residuals(mod4a) %>%
  select(- price)
```

Our final model in terms of main effects is: price ~ grade + lat + view + sqft_living














