---
title: "R Notebook"
output: html_notebook
---

```{r}
library(RPostgreSQL)
```

1.1 Local PostgreSQL connections

# source in our credential file

```{r}
home_location <- Sys.getenv("HOME")
credentials_location <- paste0(home_location, "/credentials.R")
source(credentials_location)
```

# create connection to the local wrestling database from R
# passing argument max.con = 2

```{r}
my_db_connection <- dbConnect(drv = PostgreSQL(max.con = 2), user = postgresql_username, password = postgresql_password, dbname = 'wrestling', host = 'localhost')
```

# Using R connection, write and execute a SQL query to return all the wrestlers in the wrestlers  table

```{r}

wrestlers <- dbGetQuery(conn = my_db_connection, statement = "SELECT name FROM wrestlers")
wrestlers
```

#Explore the columns stored in the table. State which data type you think each column stores.

# id INT
# born VARCHAR
# name VARCHAR
# gender VARCHAR
# win_percent REAL
# total_matches INT

```{r}
dbListTables(conn = my_db_connection)
dbListFields(conn = my_db_connection, name = "wrestlers")

```

```{r}
dbDisconnect(conn = my_db_connection)
```



xxxxxxxxxxxx        xxxxxxxxxxxxxx        xxxxxxxxxxxx
1.2 Remote PostgreSQL connections

# Store the credentials above in appropriately named variables in your credentials.R file in your home directory.
#Use your credentials to establish a connection from R to the remote database.

```{r}
home_location <- Sys.getenv("HOME")
credentials_location <- paste0(home_location, "/credentials.R")
source(credentials_location)
```


```{r}
db_connect <- dbConnect(drv = PostgreSQL(max.con = 1), user = remote_omni_postgresql_username, password = remote_omni_postgresql_password, dbname='mvhbdgdk', host='34.245.37.126')
```

#Using this R connection, write and execute a query to return all the wrestlers from the wrestlers table


```{r}
wrestlers1 <- dbGetQuery(conn = my_db_connection, statement = "SELECT * FROM wrestlers")
wrestlers1
```



```{r}
dbDisconnect(conn = my_db_connection)
```

