---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(tidyverse)
library(janitor)
```

1. Load the data, clean_names() and explore it.

```{r}
mobile_phone_reviews <- read_csv("data/20190928-items.csv") %>%
  clean_names()
mobile_phone_reviews
```


```{r}
glimpse(mobile_phone_reviews)
#unique(mobile_phone_reviews$asin)
```

2. Find the brand with the highest numbers of phones in the dataset.

```{r}
mobile_phone_reviews %>%
  group_by(brand) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(1)

  
```
Ans: Top brand is Samsung with highest number of phones!


3. For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?

```{r}
top_brand_stats <- mobile_phone_reviews %>%
  filter(brand == "Samsung") %>% #we know that top brand is Samsung
  summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )
top_brand_stats
```
The Samsung brand has 101 sample points with mean rating of 3.52 with a 0.58 deviation from the mean

```{r}
mobile_phone_reviews %>%
  filter(brand == "Samsung") %>%
  ggplot() +
  aes(x = rating, y = ..density..) +
  geom_histogram(bins = 15, col = "white")
```


```{r}
mobile_phone_reviews %>%
  filter(brand == "Samsung") %>%
  ggplot() +
  aes(x = rating) +
  geom_histogram(aes(y = ..density..), bins = 15, col = "white") +
  stat_function(
    fun = dnorm,
    args = list(
      mean = top_brand_stats$mean,
      sd = top_brand_stats$sd
    ),
    col = "red"
  )

 
```

Ans: The normal distribution appears to be a suitable model for the distribution of ratings

```{r}
library(MASS)
mobile_phone_reviews %>%
  filter(brand == "Samsung") %>%
  ggplot() +
  aes(x = rating) +
  geom_histogram(aes(y = ..density..), bins = 15, col = "white") 

fitdistr(mobile_phone_reviews$rating, "normal")
```

4. We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.

```{r}
mobile_phone_reviews %>%
  filter(rating >= top_brand_stats$mean - top_brand_stats$sd) %>%
  filter(rating <= top_brand_stats$mean + top_brand_stats$sd) %>%
  summarise(prop_within_1sd = n() / nrow(mobile_phone_reviews))

mobile_phone_reviews %>%
  filter(rating >= top_brand_stats$mean - 2*top_brand_stats$sd) %>%
  filter(rating <= top_brand_stats$mean + 2*top_brand_stats$sd) %>%
  summarise(prop_within_2sd = n() / nrow(mobile_phone_reviews))

mobile_phone_reviews %>%
  filter(rating >= top_brand_stats$mean - 3*top_brand_stats$sd) %>%
  filter(rating <= top_brand_stats$mean + 3*top_brand_stats$sd) %>%
  summarise(prop_within_3sd = n() / nrow(mobile_phone_reviews))

# The percentage of values within 1, 2 & 3 standard deviations of the mean
(pnorm(q = 1) - pnorm(q = -1))
(pnorm(q = 2) - pnorm(q = -2))
(pnorm(q = 3) - pnorm(q = -3))
```

Ans: Comparing the distribution of top brand ratings with a normal distribution, we have the following:
1std deviation 
Normal: 0.7815657	
Standard Normal: 0.6826895

Normal: 0.9330808	
Standard Normal: 0.9544997

Normal: 0.9848485		
Standard normal: 0.9973002




X X X X X X X X X X X X X X X X X X X X X X X X X X X X X X X X X X X X X

Extension

```{r}
test <- mobile_phone_reviews %>%
  filter(brand == "Samsung") 
#test
qqnorm(test$rating)
qqline(test$rating)
```

Ans: qq plot take the sample data (rating), sorts it in an ascending order and then plot it versus quantiles calculated from a theoretical distribution. The number of quantiles is selected to match the size of the sample data. 

qqnorm creates a normal Q-Q plot. 

From the above plotm we can assume that the the rating sample is normally distributed as the points appear to lie about a straight line. 


