---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidytext)
library(dplyr)
```


Text Mining Homework
1 MVP
Using the dataset austen_books() from the package janeaustenr:

a. Find the most common words in both Pride & Prejudice and Sense & Sensibility.

```{r}
library(janeaustenr)
str(prideprejudice)
```

```{r}
prideprejudice_df <- tibble(
  text = prideprejudice,
  sentence_no = 1:length(prideprejudice)
) %>%
  unnest_tokens(word, text)
```

```{r}
prideprejudice_count <- prideprejudice_df %>%
  count(word, sort = TRUE)
```

```{r}
str(sensesensibility)
```

```{r}
sensesensibility_df <- tibble(
  text = sensesensibility,
  sentence_no = 1:length(sensesensibility)
) %>%
  unnest_tokens(word, text)
```

```{r}
sensesensibility_count <- sensesensibility_df %>%
  count(word, sort = TRUE)
```



```{r}
inner_join(prideprejudice_count, sensesensibility_count, by = "word")
```


b. Find the most common words in both Pride & Prejudice and Sense & Sensibility, not including stop words.

```{r}
prideprejudice_df %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
```

```{r}
sensesensibility_df %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
```

```{r}
inner_join(
  prideprejudice_df %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE),
  sensesensibility_df %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE),
  by = "word"
)
```


c. Find the most common sentiment words in both Pride & Prejudice and Sense & Sensibility.

```{r}
prideprejudice_sentiments <- prideprejudice_df %>%
  anti_join(stop_words) %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sort = TRUE)
```

```{r}
sensesensibility_sentiments <- sensesensibility_df %>%
  anti_join(stop_words) %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sort = TRUE)
```

```{r}
inner_join(prideprejudice_sentiments, sensesensibility_sentiments, by = "word")
```

2 Extension
Taking your results above. Can you create a plot which visualises the differences between the books?

```{r}
library(ggplot2)
```

```{r}
prideprejudice_df %>%
  inner_join(get_sentiments("afinn")) %>%
  group_by(sentence_no) %>%
  summarise(avg_sentiment = mean(value)) %>%
  ggplot() +
  aes(x = sentence_no, y = avg_sentiment) +
  geom_smooth()
```




```{r}
sensesensibility_df %>%
  inner_join(get_sentiments("afinn")) %>%
  group_by(sentence_no) %>%
  summarise(avg_sentiment = mean(value)) %>%
  ggplot() +
  aes(x = sentence_no, y = avg_sentiment) +
  geom_smooth()
```












