---
title: "R Notebook"
output: html_notebook
---


```{r}
library(prob)
library(tidyverse)
library(dplyr)
library(janitor)
```

1. Load the data again, clean_names(), and re-familiarise yourself with it

```{r}
ames <- read_csv("data/ames.csv") %>%
  clean_names()
```

```{r}
#glimpse(ames)
colnames(ames)
```

2. Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?

```{r}
ames %>%
  ggplot(aes(x = lot_area)) +
  geom_histogram(bins = 200, col = "white")
  
```

Ans: Distribution appears to be normal but skewed to the right.
```{r}
popn_mean_lot_area <- ames %>%
  summarise(
    mean_lot_area = mean(lot_area)
    )

popn_mean_lot_area
```



```{r}
library(infer)
```
3. Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}
infer_resample_ames<- ames %>%
  specify(response = lot_area) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")
  
infer_resample_ames  

```


4. Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution
```{r}
infer_ci_95 <- infer_resample_ames %>%
  get_ci(level = 0.95, type = "percentile")
infer_ci_95

infer_resample_ames %>%
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = infer_ci_95)
```



5. You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?

```{r}
infer_ci_99 <- infer_resample_ames %>%
  get_ci(level = 0.99, type = "percentile")
infer_ci_99

infer_resample_ames %>%
  visualise() +
  shade_confidence_interval(endpoints = infer_ci_99)
```
Ans: Is it broader than the 95% CI due to larger area of confidence interval

6. Calculate the point estimate of the mean(lot_area)
```{r}
infer_resample_ames %>%
  summarise(mean(stat))

```


EXTENSION
Calculate a point estimate and 95% CI for the proportion of houses in the data built before 1920. Does the number of reps you use matter? [Investigate reps from 200 up to 50000, memory of your laptop permitting].

```{r}
infer_ames_1920 <- ames %>%
  mutate(before_1920 = as.numeric(year_built < 1920)) %>%
  specify(response = before_1920) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")
  
infer_ames_1920 
```

```{r}
infer_ci_95 <- infer_ames_1920 %>%
  get_ci(level = 0.95, type = "percentile")
infer_ci_95

infer_ames_1920 %>%
  summarise(mean(stat))

```

