---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(cluster)
library(factoextra)
library(dendextend)
```

```{r}
mall_customers <- read_csv("mall_customers.csv")
```


You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings.

```{r}
mall_customer_clean <- mall_customers %>%
  clean_names() %>%
  select(-customer_id)

summary(mall_customer_clean)
```


```{r}
ggplot(mall_customer_clean) + 
  aes(x = age, y = spending_score_1_100, colour = gender) +
  geom_point()
```


We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers.

```{r}
ggplot(mall_customer_clean, aes(spending_score_1_100, annual_income_k)) +
  geom_point()
```



```{r}
summary(mall_customer_clean)
```

```{r}
mall_customer_scale <- mall_customer_clean %>%
                      mutate_if(is.numeric, scale) %>%
                      select(-gender)

mall_customer_scale
```



Perform k-means clustering and chose a value of k.

```{r}
library(broom)

# Set min & max number of clusters want to look at 
max_k <- 20 

k_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(mall_customer_scale, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, mall_customer_clean)
  )

k_clusters
```


```{r}
clusterings <- k_clusters %>%
  unnest(glanced)

clusterings
```


```{r}
fviz_nbclust(mall_customer_scale, kmeans, method = "silhouette", nstart = 25)
```


```{r}
fviz_nbclust(mall_customer_scale, kmeans, method = "gap_stat", nstart = 25, k.max = 10)
```

We get that k = 6 is the optimal number of clusters 

Visualise the clustering for your chosen value of k = 6

```{r}
clusterings %>% 
  unnest(cols = c(augmented)) %>%
  filter(k == 2) %>%
 ggplot(aes(x = spending_score_1_100, y = annual_income_k, colour = .cluster, label = NULL)) +
  geom_point(aes(color = .cluster)) #+
  #geom_text(hjust = 0, vjust = - 0.5, size = 3)
```


```{r}
clusterings %>% 
  unnest(cols = c(augmented)) %>%
  filter(k <= 6) %>%
 ggplot(aes(x = spending_score_1_100, y = annual_income_k)) +
  geom_point(aes(color = .cluster)) + 
  facet_wrap(~ k)
```


Do you think the clustering seems a good fit for this data?

Ans: Yes

Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the ‘Segmentation & clustering intro’ lesson).


