---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(gtools)
library(tidyverse)
```

1. If I roll a six-sided dice once, what is the probability of getting a number less than 5?
```{r}
s <- nrow(rolldie(1))
r <- nrow(rolldie(1)%>%filter(X1<5))
p <- r/s
p

```

2. How many outcomes are there in the sample space of an experiment in which we toss three dice?
```{r}
s_three_dice <- rolldie(3)

s_three_dice %>%
  summarise(size_of_s = n())
```


3. In an experiment where we roll four dice:

a) how many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)?
```{r}
s_four_dice <- rolldie(4) 
  

total_equals_5_6_7 <- s_four_dice %>%
  mutate(total = X1 + X2 + X3 + X4) %>%
  filter(total >=5 & total <=7) %>%
  summarise(count = n()) 

total_equals_5_6_7  


```


b) what is the probability of this event?
```{r}
s <- nrow(s_four_dice)
r <- total_equals_5_6_7
p <- r/s
p
```

c) what assumptions do we apply in answering part ii?

Ans: repetition allowed


4. Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?
```{r}
five_chair_permutations <- permutations(n = 5,
                                        r = 5,
                                        v = c(1:5),
                                        repeats.allowed = FALSE)

probability_decreasing_height <- 1 / nrow(five_chair_permutations)
probability_decreasing_height
```


5. I roll six dice:

a) what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?

```{r}
s_six_dice <- rolldie(6) 

given_order <- c(6,5,4,3,2,1)

six_to_one_order <- s_six_dice %>%
  mutate(check_order = isin(s_six_dice, given_order, ordered = TRUE)) %>%
  filter(check_order == TRUE)

six_to_one_order

prob_given_order <- nrow(six_to_one_order) / nrow(s_six_dice)
prob_given_order

```

b) what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?
```{r}
six_to_one_no_order <- s_six_dice %>%
  mutate(check_order = isin(s_six_dice, given_order)) %>%
  filter(check_order == TRUE)

six_to_one_no_order

prob_given_order <- nrow(six_to_one_no_order) / nrow(s_six_dice)
prob_given_order
```

6. If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?

Ans:
event A: single card drawn - black
event B: spades suit drawn

P(A|B) = P(AnB) / P(B)

P(AnB) = P(A) x P(B)

P(A) = 13/26

P(B) = 26/52

P(A|B) =(13/26 * 26/52) / 26/52
        = 0.5

```{r}

```






