---
title: "R Notebook"
output: html_notebook
---

HOMEWORK DAY 1
1. Read in the state_income_data.csv file using the appropriate function.

```{r}
library(readr)
```


```{r}
state_income_data <- read_csv("data/state_income_data.csv")
state_income_data
```


2. How do you specify your own column names when using read_csv()?

Answer: By using specifying a character vector to argument col_names.

3. Read in the cars.csv file and use the col_types() function to ensure you load in:
X1 as character
mpg, cyl, disp, hp as double
vs as logical

```{r}
#raw_cars <- read_csv("data/cars.csv")
raw_cars2 <- read_csv("data/cars.csv", col_types = cols(X1 = col_character(), vs = col_logical()))
raw_cars2
```


4. Read in the scotland.txt file using the appropriate function.

```{r}
#raw_scot <- read_tsv("data/scotland.txt")
#raw_scot
raw_scot <- read_delim("data/scotland.txt", delim = ";")
raw_scot
```


5. How do you read text into a one element character vector?

Answer: Using read_file() 

6. Read in the steam-200k-sample.csv file. Fix any problems you may encounter.

```{r}
raw_steam_sample <- read.csv("data/steam-200k-sample.csv", skip = 2)
raw_steam_sample
```


7. Read in the historic_eu_payments.tsv file.

```{r}
raw_hist <- read_tsv("data/historic_eu_payments.tsv")
raw_hist
```


8. How do you read lines of text into a multi-element text vector?

Answer: Using read_lines("file_name.txt")


9. Read in the JSON file from the following url: http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt

```{r}
library(jsonlite)
library(readr)
```

```{r}
raw_file <- read_file("http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")
prettify(raw_file)
file <- parse_json(raw_file)
file
```

