---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)

```

# 2 project_management analysis

# Load the data into a dataframe project


```{r}
project <- read_csv("../data/project_management.csv")
```

# Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.

```{r}
project %>%
  ggplot(aes(estimated_length, actual_length)) +
  geom_point()

```


# Label the data points with their row number in the data frame using geom_text() [Hint - you can pass aes(label = 1:nrow(project)) to this layer to generate row index labels]

```{r}
project %>%
  ggplot(aes(estimated_length, actual_length)) +
  geom_point() +
  geom_text(aes(label = 1:nrow(project)), nudge_x = 0.25, check_overlap = TRUE)
```

# Identify by eye any points you think might be outliers and note their labels.

Outliers: 5, 18, 24

# Further split your outliers into those you think are ‘influential’ or ‘non-influential’ based on a visual assessment of their leverage.

Influencial : 24, 18
Non-Influencial : 5


# Regress actual_length on estimated_length and confirm your visual assessment of which points are ‘influential’ or ‘non-influential’ outliers based on Cook’s distance. You can get a useful plot of Cook’s distance by passing argument which = 4 to autoplot(). Or try the base R plot() function for comparison [e.g. plot(model)]!

```{r}
library(ggfortify)
model <- lm(actual_length ~ estimated_length, data = project)
autoplot(model, which = 4)
```

Obtain the intercept and regression coefficient of variable estimated_length for a simple linear model fitted to data omitting one of your non-influential outlier points.
```{r}
refunds_no_outliers <- refunds %>%
  filter(is_outlier == FALSE)
```



```{r}
summary(model)

```


How different are the intercept and coefficient from those obtained above by fitting the full data set? Does this support classifying the omitted point as non-influential?
Plot the data points, this regression line and the regression line for the full data set. How different are the lines?












