---
title: "R Notebook"
output: html_notebook
---

2.2 if statements and functions

2.2.1
Write a function which multiplies all numbers by 15 and adds 4
```{r}
multiply_add <- function(x){
  return(x * 15 + 4)
}
multiply_add(3)
```


2.2.2
Write a function that returns “bird”, if the input is “goose”, “duck” or “pigeon”, and returns “not bird” for all other input.
```{r}
bird <- c("goose", "duck", "pigeon")
bird_check <- function(x){
  if(x %in% bird){
    print("bird") 
  } else{
    print("Not bird")
  }
}
bird_check("goose")
```

2.2.3
Write a function which multiplies all numbers by 10. If the input isn’t a number, the function should return “Invalid input”.
```{r}
multiply_by_10 <- function(x){
  if(is.numeric(x)){
   x * 10 
  } else{
    print("Invalid inpiut")
  }
  
}
multiply_by_10("x")
```


2.3
2.3.1
For the vector below, make a new vector which is equal to “Big” every time the element of sizes is greater than 10, and equal to “Small” every time the element of sizes is less than or equal to 10.

```{r}
sizes <- c(13, 15, 10, 8, 22)
size_text <- ifelse(sizes > 10, "Big", "Small")
size_text


```


2.3.2
For the vector below convert:
apple → alpaca
banana → bonobo
cherry → chipmunk

```{r}
x <- as.factor(c("apple", "banana", "cherry"))
dplyr::recode(x, "apple" = "alpaca", "banana" = "bonobo", "cherry" = "chipmunk")
```

2.3.3
The two vectors below show the ages at marriage of each member of a couple. The first elements of each vector correspond to the first couple, the second elements to the second couple, and so on.
Create a new vector which is equal to:
“Wife older” whenever the wife’s age is highest “Husband older” when the husband’s age is highest “Same age” when they are the same age


```{r}
library(dplyr)
wife_age <- c(29L, 30L, 36L, 31L, 22L)
husband_age <- c(28L, 35L, 32L, 31L, 29L)
case_when (
  wife_age > husband_age ~ "Wife older",
  husband_age > wife_age ~ "Husband older",
  TRUE ~ "Same age"
)

```

2.4

```{r}
my_list <- list(
  4,
  "apple",
  10.5,
  c("is", "an", "apple"),
  "apple",
  c("i", "like", "apples"),
  8
)
```

2.4.1
Use a loop to print out every element of my_list which is of type character. Decide if you need a for loop or a while loop.

```{r}
for(item in my_list){
  if(is.character(item)){
     print(item)
  }
}
length(item[2])
```

2.4.2
Once again write a loop that prints out character elements. This time if the element has a length() greater than one, paste() all the elements in that vector together into one big character vector.

```{r}

for(item in my_list){
  if(is.character(item)){
    if(length(item) > 1){
      print(paste(item, collapse = " "))
      
    }else {
      print(item)
    }
  }
}


```





