---
title: "R Notebook"
output: html_notebook
---
#1. PREPARATION
Investigate table relationships: look for primary keys and foreign keys, see if you can spot any one-to-one, one-to-many or many-to-many relationships.

Answer:
Committees Table -> committee_id is Primary Key
Employees_Committee Table -> committee_id is Foreign Key


```{r}
library(RPostgreSQL)

home_location <- Sys.getenv("HOME")
credentials_location <- paste0(home_location,"/credentials.R")
source(credentials_location)

db_connect <- dbConnect(drv = PostgreSQL(), user = postgresql_username, password = postgresql_password, dbname = "omni_employees", host = "localhost")

rm(postgresql_username, postgresql_password)
```

2. MVP

1. Find all the employees who work in the ‘Human Resources’ department.

```{sql connection=db_connect}
SELECT *
FROM employees
WHERE department = 'Human Resources'
```

2. Get the first name, last name, and country of the employees who work in the ‘Legal’ department

```{sql connection=db_connect}
SELECT 
  id,
  first_name,
  last_name,
  country
FROM employees
WHERE department = 'Legal'
```


3. Count the number of employees based in Portugal.

```{sql connection=db_connect}
SELECT 
  COUNT(*) AS portugal_employees
FROM employees
WHERE country = 'Portugal'
```


4. Count the number of employees based in either Portugal or Spain.

```{sql connection=db_connect}
SELECT 
  COUNT(*) AS emp_Portugal_Spain
FROM employees
WHERE country IN('Portugal', 'Spain')
```


5. Count the number of pay_details records lacking a local_account_no

```{sql connection=db_connect}
SELECT *
FROM pay_details
ORDER BY local_account_no ASC NULLS FIRST

```

```{sql connection=db_connect}
SELECT 
COUNT(id) AS no_account_no
FROM pay_details
WHERE local_account_no IS NULL
```


6. Are there any pay_details record lacking both a local_account_no and iban number?

```{sql connection=db_connect}
SELECT 
COUNT(id) AS no_account_no
FROM pay_details
WHERE local_account_no IS NULL AND iban IS NULL
```

7. Get a list of employees first names and last names ordered alphabetically by their last name (put any nulls last).

```{sql connection=db_connect}
SELECT 
  first_name,
  last_name
FROM employees
ORDER BY last_name ASC NULLS LAST
```

8. Get a list of employees first names, last names and countries, ordered alphabetically first by their country and second by their last name (put any nulls last).

```{sql connection=db_connect}
SELECT 
  first_name,
  last_name,
  country
FROM employees
ORDER BY country ASC, last_name ASC NULLS LAST
```


9. Find the top ten highest paid employees in the corporation.

```{sql connection=db_connect}
SELECT * FROM employees
WHERE salary IS NOT NULL
ORDER BY salary DESC NULLS FIRST 
LIMIT 10
```

10. Find the first name, last name and salary of the lowest paid of the employees in Hungary

```{sql connection=db_connect}
SELECT *
FROM employees
WHERE country = 'Hungary'

```


```{sql connection=db_connect}
SELECT 
  first_name,
  last_name,
  salary
FROM employees
WHERE salary IS NOT NULL AND country = 'Hungary'
ORDER BY salary DESC

```


11. How many employees have a first name beginning with ‘F’?

```{sql connection=db_connect}
SELECT 
COUNT(id) AS First_name_begining_with_F
FROM employees
WHERE first_name LIKE 'F%'
```

12. Find all the details of any employees with a ‘yahoo’ e-mail address?

```{sql connection=db_connect}
SELECT *
FROM employees
WHERE email LIKE '%yahoo%'
```


13. Count the number of pension enrolled employees not based in either France or Germany.

```{sql connection=db_connect}
SELECT 
COUNT(id) AS pension_enrolled_employees
FROM employees
WHERE pension_enrol IS TRUE AND country NOT IN('France', 'Germany')

```


14. Breakdown the numbers of employees enrolled, not enrolled and whose enrollment status is unknown in the corporation pension scheme.

```{sql connection=db_connect}
SELECT 
DISTINCT(pension_enrol),
COUNT(*)
FROM employees
--WHERE country = 'United States'
GROUP BY pension_enrol
```

15. What is the maximum salary among employees in the Engineering department who work 1.0 full-time equivalent hours?

```{sql connection=db_connect}
SELECT
MAX(salary) AS max_sal_engineering
FROM employees
WHERE department = 'Engineering' AND fte_hours = 1.0

```

16. Obtain a count by department of the employees who started work with the corporation in 2003.

```{sql connection=db_connect}
SELECT
department,
COUNT(id) AS total_people_started_in_2003
FROM employees
WHERE start_date BETWEEN '2003-01-01' AND '2003-12-31'
GROUP BY department
```




```{r}
dbDisconnect(db_connect)
```

