---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---


2 MVP

Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.
```{r}
library(ggplot2)
library(CodeClanData)
library(tidyverse)
```


```{r}
backpack
dim(backpack)
glimpse(backpack)
```


Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
ggplot(backpack) +
  geom_bar(aes(x = backpack_weight), fill = "light blue") +
  labs(
    x = "\nBackpack Weight (kg)",
    y = "Count",
    title = "Backpack Weight Distribution"
  )

```


Question 3.

Are there differences in backpack weight between sex?

```{r}
ggplot(backpack) +
  geom_bar(aes(x = backpack_weight, fill = sex), position = "dodge") +
  labs(
    x = "\nBackpack Weight (kg)",
    y = "Count",
    title = "Backpack Weight Distribution by Gender",
    fill = "Sex"
  )
```


Question 4.

What is the relationship between body weight and backpack weight?

```{r}
ggplot(backpack) +
  geom_col(aes(x = backpack_weight, y = body_weight), fill = "blue") +
  labs(
    x = "\nBackpack Weight (kg)",
    y = "Body Weight (lbs)",
    title = "Backpack Weight Distribution by Body Weight",
    fill = "Sex"
  )
```


Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
ggplot(backpack) +
  geom_col(aes(x = backpack_weight, y = body_weight, fill = sex), position = "dodge") +
  labs(
    x = "\nBackpack Weight (kg)",
    y = "Body Weight (lbs)",
    title = "Backpack Weight Distribution by Body Weight",
    fill = "Sex"
  ) +
  facet_wrap(~ sex)
```


Question 6.

What proportion of students report back pain?

```{r}
proportion_backpain <- backpack %>%
  group_by(back_problems) %>%
  summarise(count = n())

ggplot(proportion_backpain) +
  geom_bar(aes(x = " ", y = count, fill = back_problems), width = 0.5, stat = "identity") +
  xlab("Back Problems") 
  
```


Question 7.

Is this proportion different between men and women?

```{r}
proportion_backpain <- backpack %>%
  select(sex, back_problems) %>%
  group_by(back_problems, sex) %>%
  summarise(count = n())

ggplot(proportion_backpain) +
  geom_bar(aes(x = back_problems, y = count, fill = sex), width = 0.5, stat = "identity") +
  xlab("Back Problems") +
  scale_x_continuous(breaks = c(0,1))
  
```


Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.

```{r}
ggplot(backpack) +
  geom_bar(aes(x = backpack_weight), fill = "light blue") +
  labs(
    x = "\nBackpack Weight (kg)",
    y = "Count",
    title = "Backpack Weight Distribution"
  )


```



3 Extensions


Question 1.

Does reported backpain differ across the year groups? Ignore year 0 in your data.

Question 2.

Is there a difference between how heavy the bags those in different years carry?

